Parsing Postfix log files

### 2007-04-10 doc/logparser.tex
Added a run down of the contents of the paper in the introduction.

XXX MAYBE EXPLAIN WHAT WILL BE IN THE FOLLOWING SECTIONS??? XXX

@@

@@

@@

@@

@@

@@

>>>>

Section~\ref{background} provides background information about: the
motivation for this project; the Postfix Mail Transport Agent; a short
overview of the parser; the assumptions inherent in the design of the
algorithm and program; and a list of other Postfix log parsers.

Section~\ref{rules} discusses the parsing rules in detail, explaining their
structure, giving an example rule and sample data it matches successfully
against.

Section~\ref{parsing-algorithm} contains the meat of the paper, describing
a naive parsing algorithm and the complications encountered which shaped
the full algorithm, followed by a comprehensive explanation of the
different stages of the algorithm and the actions taken during the
execution of the algorithm.

Section~\ref{limitations-improvements} lists the limitations of the program
and/or the algorithm, then suggests some ways of dealing with the
limitations, with the goal of improving parsing and reproducing the journey
a mail takes through the internals of Postfix.

Section~\ref{conclusion} describes the results of the project to date.  XXX
IMPROVE THIS.

Section~\ref{references} catalogues resources used in developing the
algorithm, writing the program and preparing this paper.  
Any resources referred to in the paper are also given, plus some additional
resources expected to be helpful in understanding Postfix, anti-spam
techniques, or the paper.

@@

\label{background}

@@

\label{rules}

@@

\label{parsing-algorithm}

@@

\label{limitations-improvements}

@@

\label{conclusion}

@@

\label{references}

XXX ADD RESOURCES ONCE THE PAPER IS REASONABLY COMPLETE AND THEN REFERENCE
THEM FROM WITHIN THE PAPER XXX
